The Aquarius Co-Moving Group is Not a Disrupted Classical Globular Cluster\altaffilmark{1}

### 2013-08-13 2012-aqs/draft-aqs.tex
Aquarius updated.

%!TEX TS-program = pdflatex
\documentclass{emulateapj}

\usepackage{amssymb,graphics} % for resolution symbol
\usepackage{longtable,booktabs,multirow}
\usepackage{pdflscape,rotating}
\usepackage{wasysym} % for \astrosun

\maxdeadcycles=1000

\shorttitle{No Evidence for the Aquarius Co-Moving Group Resulting from a Disrupted Classical Globular Cluster}
\shortauthors{Casey et al}

@@

\title{No Evidence for the Aquarius Co-Moving Group \\Resulting from a Disrupted Classical Globular Cluster\altaffilmark{1}}

@@

\author{Andrew R. Casey\altaffilmark{2,3}, Stefan Keller\altaffilmark{2}, Alan Alves-Brito\altaffilmark{2}, Anna Frebel\altaffilmark{3}, Gary Da Costa\altaffilmark{2}, Amanda Karakas\altaffilmark{2}, David Yong\altaffilmark{2}, Kevin Schalufman\altaffilmark{3}, Heather Jacobson\altaffilmark{3}, QinQin Yu\altaffilmark{3}, Ken Freeman\altaffilmark{2}, Cherie Fishlock\altaffilmark{2}}
\altaffiltext{1}{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observatory, Chile.}
\altaffiltext{2}{Research School of Astronomy \& Astrophysics, Australian National University, Mount Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia; acasey@mso.anu.edu.au}
\altaffiltext{3}{Massachusetts Institute of Technology, Kavli Institute for Astrophysics and Space Research,
77 Massachusetts Avenue, Cambridge, MA 02139, USA}

\begin{abstract}
We present a detailed analysis of high S/N, high-resolution spectra for five Aquarius stream stars observed using the MIKE spectrograph on the Magellan Clay telescope. Our sample represents one third of the total number of published stream members. We find the co-moving group is not chemically coherent; a wide metallicity dispersion ranging from {$\mbox{[Fe/H]} = -0.63$} to $-1.63$\,dex is observed. Enhanced [Na/Fe], [Ni/Fe] and [$\alpha$/Fe] abundance ratios suggest the co-moving group is not the result of a disrupted dwarf galaxy. Additionally, we find no evidence that the stream is a result of a disrupted classical globular cluster, contrary to a previously published claim. No inverse Na-O correlation is present, and we find a strong positive Mg-Al relationship similar to that observed in the thick disc. The group is chemically indistinguishable from Milky Way field stars with the exception of one candidate, C222531-145437. From positions, velocities, and detailed chemical abundances it is unambiguous that C222531-145437 is a tidal remnant from the $\omega$-Centurai globular cluster. We hypothesise the co-moving group is galactic in origin, and is a result from a disc-satellite perturbation in the Milky Way thick disc. Derived orbits, $u$--$v$ plane velocities, and angular momentum calculations for Aquarius candidates qualitatively supports our hypothesis, and are consistent with a disc interaction on the order of a few Gyr ago. Given the debris of C222531-145437 as tidal debris,  $\omega$-Centurai is a plausible perturber, as is the Sagittarius dwarf. While there is no evidence that the Aquarius stream is the tidal tail of a disrupted satellite, we advocate the `Aquarius group' as a more appropriate description. Like the Canis Major over-density, and the Hercules and Monoceros groups, the Aquarius co-moving group adds to the list of kinematically-identified substructures that are not actually accreted material; they are simply part of the rich complexity of the Milky Way structure.
\end{abstract}

@@

\section{Introduction}
Galaxies are hierarchically formed through chaotic mergers of smaller systems. The Milky Way is no exception. The accumulating stellar debris in our own galactic halo provides ongoing evidence for such merging events. As accreting satellites infall onto the galaxy, tidal forces disrupt the smaller system, hurtling stars in leading and trailing directions. Unsurprisingly the velocities of stars within these `stellar streams' are sensitive to the galactic potential. As such, their phase-space information can collectively constrain the fraction and distribution of accreted matter in the galaxy, the sub-halo mass function, as well as the shape and extent of dark matter in the Milky Way. Moreover, individual chemical abundances from high-resolution spectra can trace the chemical evolution of the galaxy.
% can constrain the  precise nucleosynthesis sites where elements are forged, as well as

% Consider adding a final sentence about the amount of work that has gone into stellar streaams
Wide-field deep imaging surveys have proved excellent sources for finding stellar streams. Dozens have been identified through careful photometric selections and matched-filtering techniques, with some to a galactocentric distance of 100\,kpc \citep{belokurov;et-al_2007,drake;et-al_2013}. Indeed, it is clear that a large fraction of the stellar halo has been built up by accretion. However, as \citet{helmi;white_1999} point out, these detection strategies are only successful for identifying streams that are sufficiently distant from the solar neighbourhood. A nearby stream, within $\sim$10\,kpc, will not appear as a photometric over-density as the stars would be sparsely positioned across the sky. Such substructures would only be detectable by their kinematics, or perhaps with precise elemental abundances through a `chemical tagging' approach (e.g. see \citet{freeman;bland-hawthorn_2002}).

% Talk about RAVE
It is therefore necessary to spectroscopically survey the solar neighbourhood stars to reveal any nearby substructures. The Radial Velocity Experiment (RAVE) team began such a survey in 2003 and have observed spectra from over 500,000 stars across 17,000\,deg$^{2}$. As the name hints, the primary goal of RAVE was to obtain radial velocities for the solar neighbourhood and beyond. In an attempt to remain kinematically unbiased, RAVE candidates were selected solely by their apparent magnitude. With the exception of bulge stars, where some photometric cuts were employed, all stars between $9 < I < 13$ were observed. Almost all of these candidates have published radial velocity measurements \citep{steinmetz;et-al_2006}, and for a subset of stars with a sufficient Signal-to-Noise ($S/N$) ratio, estimates of stellar parameters have been derived using a $\chi^2$ minimisation technique \citep{zwitter;et-al_2008, siebert;et-al_2011}.

% Identification of the aquarius stream
Using these data, \citet{williams;et-al_2011} identified a co-moving group of nearby (${0.5\,\mbox{kpc} \lesssim d \lesssim 10\,\mbox{kpc}}$) stars in the vicinity of the Aquarius constellation ${(l, b) = (60\,^\circ, -55\,^\circ)}$. Thus, the co-moving group was named the Aquarius stream. The group is most apparent when examining velocities against galactic latitude for stars within $-70\,^\circ < b < -50\,^\circ$. \citet{williams;et-al_2011} employed a selection criteria of $-250\,\mbox{km s}^{-1} < V_{\rm hel} < -150\,\mbox{km s}^{-1}$, $30\,^\circ < l < 75\,^\circ$ and $J > 10.3$ to maximize the contrast between the stream and background, identifying 15 candidates in the process. The average heliocentric velocity of these members was found to be $V_{\rm hel} = -199\,\mbox{km s}^{-1}$, with a dispersion of 27\,km s$^{-1}$. The radial velocity uncertainties provided by the RAVE catalog are described to be $\sim$2\,km s$^{-1}$, so the stream's wide kinematic distribution appears to be real.

% QUANTIFYING THE STREAM DETECTION
Upon examining the galactic longitude and velocities of Aquarius stars, the stream appears quite distinct from the halo. In order to quantify the statistical likelihood that the Aquarius stream is truly separate from a smooth halo distribution, \citet{williams;et-al_2011} compared the number of observed RAVE stars within $-70\,^\circ < b < -50\,^\circ$ against the Galaxia \citep{sharma;et-al_2011} and Besan\c{c}on \citep{robin;et-al_2003} galaxy simulations. The predicted particles in each model between $-70\,^\circ < b < -50\,^\circ$ were binned in $\Delta{l} \times \Delta{V_{\rm hel}}$ blocks using varying grid cell sizes between $25\,^\circ$ to $70\,^\circ$ and $20\,\mbox{km s}^{-1}$ to $100\,\mbox{km s}^{-1}$. The RAVE sample was binned in the same way, discretising the inferred statistical significance of the observed over-density. \citet{williams;et-al_2011} found the stream to be significant ($>4\sigma$) in 96\% of the cell proportions employed for the Besan\c{c}on model. By sampling the Galaxia model repeatedly with varying extinction rates, a similar result was found: between $75\pm15$\,\% to $80\pm18$\,\% of grid cells showed the Aquarius stream to be significant at the $4\sigma$ level or higher. Given the high-latitude and proximity of the stream, it is not surprising that dust had a negligible effect on the statistical significance. \citet{williams;et-al_2011} concluded that the over-density in $l, V_{\rm hel}$ is a true substructure, and neither the choice of galaxy model, cell dimension, nor the extinction rate made any real difference to the detection significance.

% STREAM IS LOCALIZED
% the stream appears to be quite localized in space.
% nearby streams could be strewn out over several degrees. the Orphan stream wraps over 60 degrees in the sky, and the Sgr stream wraps several steradians

% DISTANCE AND DYNAMICS
% heliocentric + galactic velocities suggest the aquarius stream stars are in the halo, and not associated with the disc.
% distances

The Sagittarius stream is arguably the most prominent ongoing accretion event in the galaxy. Given the extent of stellar debris the Sagittarius dwarf spheroidal (dSph) galaxy has littered throughout the Milky Way, it is reasonable to suspect the Aquarius stream might originate from the Sagittarius dwarf. Indeed, the Aquarius  stars do not lie far from the orbital plane of Sagittarius and the metallicities reported by \citet{williams;et-al_2011} are not dissimilar from the Sagittarius stream. However, \citet{williams;et-al_2011} found the Aquarius transverse motions (specifically $V_{Z}$ and $V_\phi$) to be quite distinct from Sagittarius. Based on the phase space information available, \citet{williams;et-al_2011} concluded that the newly discovered stream could not be positively associated with the Monoceros stream, Hercules-Aquila cloud, or either the Canis Major or Virgo over-densities.

RAVE observations suggest the Aquarius stream has a metallicity of $\mbox{[Fe/H]} \sim -1.0$, slightly more metal-rich than halo stars at the same distance. Using stellar parameters from the RAVE pipeline, \citet{williams;et-al_2011} found the stream to have an average of ${\mbox{[M/H]} = -1.0 \pm 0.4}$\,dex, compared to ${\mbox{[M/H]} = -1.1 \pm 0.6}$\,dex for background stars after the same selection cuts had been employed. Of the 15 Aquarius stars in the \citet{williams;et-al_2011} discovery sample with stellar parameters, the metallicity range from medium-resolution spectroscopy is wide: between --2.02 and {--0.33\,dex}. High-resolution spectroscopic observations with high $S/N$ are necessary to accurately characterise the stream's metallicity distribution.

To this end, \citet{wylie-de-boer;et-al_2012} obtained high-resolution ($\mathcal{R} = 25,000$) spectra with modest $S/N$ ($\sim$30 pixel$^{-1}$) for six Aquarius stream stars using the echelle spectrograph on the ANU 2.3m telescope. Their data indicate a surprisingly  narrow metallicity distribution compared to the RAVE results: ${\mbox{[Fe/H]} = -1.09 \pm 0.10}$\,dex extending from ${\mbox{[Fe/H]} = -1.25}$ to {--0.98\,dex}. Observations of such minimal chemical scatter from stars that share a common origin is typically noted only in either globular or open clusters. The largest [Fe/H] discrepancy between the \citet{williams;et-al_2011} and \citet{wylie-de-boer;et-al_2012} study was ${\Delta\mbox{[Fe/H]} = -0.66}$\,dex for the most metal-rich star in the \citet{williams;et-al_2011} sample. The most metal-poor star in the \citet{williams;et-al_2011} study was not observed by \citet{wylie-de-boer;et-al_2012}.

In addition to ascertaining stellar parameters, \citet{wylie-de-boer;et-al_2012} measured elemental abundances for the Aquarius stream stars -- the only study to do so until now. The authors primarily focussed on light elements: Na, O, Ni, Mg, and Al. Chemical patterns in these elements arise as natural consequences of nucleosynthetic processes in massive stars and have been repeatedly observed in globular clusters. Specifically, an anti-correlation between sodium and oxygen content appears ubiquitous to globular cluster stars. While the exact formation mechanism is still under debate, the chemical relationship is well-established empirically. The {Na-O} pattern provides the best chemical evidence that their enrichment history has been dominated by Type \textsc{ii} supernova (SN) events, and that those stars formed in a globular cluster-like environment.

% The following text was placed before 'While the ...'
%Originally this relationship was thought to arise from internal mixing along the giant branch. However, dwarf globular cluster stars were found to exhibit strong Na-enhancement and O-depletion, contrary to what would be expected if the Na-O anti-correlation was purely a result of internal mixing. It is well known now that photospheric abundance variations resulting from internal mixing are limited to carbon, nitrogen and lithium. Additionally, light element variations can be explained by classic nucleosynthetic pathways, albeit extreme temperatures are necessary for such relationships to arise -- much higher than would reasonably be expected in globular cluster stars. Several descriptions for an astrophysical site that would permit such nucleosynthetic processes have been hypothesized, including massive intermediate-mass Asymptotic Giant Branch (AGB) binary stars \citep{de_mink;et-al_2009} and fast-rotating massive stars \citep{decressin;et-al_2007}.

From high-resolution spectroscopy of six Aquarius stars, four of which have sodium and oxygen abundance measurements, \citet{wylie-de-boer;et-al_2012} found two stars with enhanced sodium; slightly higher [Na/Fe] ratios than halo stars of the same metallicity. However, no strong oxygen depletion was evident in the data. Thus, although they found minimal chemical scatter in the overall metallicities of Aquarius stream stars, they observed no evidence of a {Na-O} inverse correlation.

There are other chemical abundance patterns that allow us to infer the stream's chemical enrichment environment. \citet{nissen;schuster_1997} first noted that nearby solar neighbourhood stars were enriched in [Ni/Fe] and [Na/Fe]. \citet{fulbright_2000} came to a similar conclusion: only somewhat distant ($R_\odot > 20$\,kpc) stars are likely to be sodium deficient. If the stellar halo has been built up from the accretion of smaller dwarf satellites, \citet{nissen;schuster_1997} proposed that this chemical trend may be indicative of the halo merger history since stars at larger $R_\odot$ are more likely to have been accreted rather than formed in-situ. \citet{wylie-de-boer;et-al_2012} found all the Aquarius stars in their sample to be enriched in both sodium and nickel; contrary to what would be expected if the stars originated from a disrupted dSph galaxy. If the stream had originated from an accretion event, this provides an indication that the stars were first enriched in a globular cluster-like environment.

Combined with the low level of chemical scatter present in their sample, these chemical indicators led \citet{wylie-de-boer;et-al_2012} to conclude that the Aquarius stream is the result of a tidally disrupted globular cluster. \citet{williams;et-al_2011} had previously precluded this possibility with any known clusters after modelling an Aquarius-like progenitor infalling onto the Milky Way and comparing the predicted $l, b, V_{\rm hel}$ with known, nearby globular clusters of similar metallicities. No known globular cluster could match their simulation. If both scenarios are accurate then the undiscovered disrupting cluster might still remain and would be very close, such that it is unlikely it would not have been discovered by now.

We seek to investigate the nature of the Aquarius stream, specifically the recent globular cluster origin claim made by \citet{wylie-de-boer;et-al_2012}. We present a detailed analysis for five Aquarius stream candidates from high-resolution, high $S/N$ observations taken using the Magellan Inamori Kyocera Echelle spectrograph \citep{bernstein;et-al_2003} with the Magellan Clay telescope. Details of the observations and data reduction are outlined in the following section. The data analysis is chronicled in Section \ref{sec:analysis} and a detailed discussion of these results resides in Section \ref{sec:discussion}. In Section \ref{sec:conclusions} we present a summary of our conclusions and critical interpretations.

\begin{deluxetable*}{lcccccccccc}
\tablecolumns{1}
\tabletypesize{\scriptsize}
\tablecaption{Observations\label{tab:observations}}
\tablehead{
	\colhead{Designation} &
	\colhead{$\alpha$} &
	\colhead{$\delta$} &
	\colhead{Observed} &
	\colhead{Airmass} &
	\colhead{Seeing} &
	\colhead{$t_{exp}$} &
	\colhead{S/N\tablenotemark{a}} &
	\colhead{$V_{\rm hel}$} &
	\colhead{$V_{\rm err}$} \\
 & (J2000) & (J2000) & Date & & (") & (secs) & (px$^{-1}$) & (km s$^{-1}$) & (km s$^{-1}$)
}
\startdata

\\ \multicolumn{11}{c}{Standard Stars} \\ \hline \\
HD\,41667		& 06:05:03.7 & $-$32:59:36.8		& 2011-03-13	& 1.005	& 1.0 & 90 		& 340 & 297.1 		& 0.1 \\
HD\,44007		& 06:18:48.6 & $-$14:50:44.2 		& 2011-03-13	& 1.033	& 1.0 & 120		& 280 & 161.8 		& 0.1 \\
HD\,76932		& 08:58:44.2 & $-$16:07:54.2		& 2011-03-14	& 1.158	& 1.0 & 25		& 330 & 117.8		& 0.1 \\
HD\,136316		& 15:22:17.2 & $-$53:14:13.9		& 2011-03-14	& 1.118	& 0.9 & 120 	& 400 & $-$38.8 	& 0.1 \\
HD\,141531		& 15:49:16.9 & $+$09:36:42.5	& 2011-03-14	& 1.309	& 0.9 & 120	& 350 & 2.8			& 0.1 \\
HD\,142948		& 16:00:01.6 & $-$53:51:04.1		& 2011-03-14	& 1.107	& 1.0 & 90 	& 320 & 29.9 		& 0.1 \\
\hline

\\ \multicolumn{11}{c}{Program Stars} \\ \hline \\
C222531-145437	& 22:25:31.7 & $-$14:54:39.6	& 2011-07-30	& 1.033	& 0.8	& 650 & 135	& $-$156.4 & 0.1 \\
C230626-085103	& 23:06:26.6 & $-$08:51:04.8	& 2011-07-30	& 1.096	& 1.0	& 650 & 100	& $-$221.1 & 0.1 \\
J221821-183424	& 22:18:21.2 & $-$18:34:28.3	& 2011-07-30	& 1.026	& 0.9 	& 650 & 115	& $-$159.5 & 0.1 \\
J223504-152834	& 22:35:04.5 & $-$15:28:34.9	& 2011-07-30	& 1.047	& 1.0 	& 650 & 130	& $-$169.7 & 0.1 \\
J223811-104126	& 22:38:11.6 & $-$10:41:29.4	& 2011-07-30	& 1.218	& 1.2 	& 650 & 115	& $-$235.7 & 0.1

@@

\section{Observations \& Data Reduction}

The most complete sample of Aquarius stream stars is presented in the discovery paper of \citet{williams;et-al_2011}. Our sample includes five stars: four common to the \citet{wylie-de-boer;et-al_2012} study, and an additional candidate from the original \citet{williams;et-al_2011} sample. The supplementary star, C2306265-085103, was observed by the RAVE survey but had a $S/N$ ratio too low for stellar parameters to be accurately determined. All program stars were observed in July 2011 in reasonable seeing at low airmass (Table \ref{tab:observations}), and six  standard stars were observed in March 2011. All observations were taken using a 1.0'' slit, providing a spectral resolution in excess of $\mathcal{R} = 28,000$ in the blue arm and $\mathcal{R} = 22,000$ in the red arm. The exposure time for our program stars was 650\,seconds per star in order to ensure a $S/N$ ratio in excess of 100\,pixel$^{-1}$ at 600\,nm.

Calibration frames were taken at the start of each night, including twenty flat-field frames (10 quartz, 10 milky) and 10 Th-Ar arc lamp exposures for wavelength calibration. The data were reduced using the CarPy pipeline\footnote{http://code.obs.carnegiescience.edu/mike}. One standard star, HD\,41667, was also reduced using standard extraction and calibration methods in \textsc{iraf}. The resultant spectra from both approaches were compared for residual fringing, $S/N$, and wavelength calibration. No noteworthy differences were present, and the CarPy pipeline was utilised for the remainder of the data reduction. Each reduced echelle order was carefully normalised using a third order spline with defined knot spacing. Normalised orders were stitched together to provide a single one-dimensional spectrum from 333-916\,nm.

>>>>

%!TEX TS-program = pdflatex
\documentclass[iop]{emulateapj}

\usepackage{amssymb,graphics} % for resolution symbol and \blacktriangledown
\usepackage{longtable,booktabs,multirow}
\usepackage{wasysym} % for \astrosun

\maxdeadcycles=1000
\setcounter{secnumdepth}{5}

\shorttitle{The Aquarius Co-Moving Group is Not a Disrupted Classical Globular Cluster}
\shortauthors{Casey et al}

@@

\title{The Aquarius Co-Moving Group is Not a Disrupted Classical Globular Cluster\altaffilmark{1}}

@@

\author{Andrew R. Casey\altaffilmark{2,3}, Stefan Keller\altaffilmark{2}, Alan Alves-Brito\altaffilmark{2,4}, Anna Frebel\altaffilmark{3}, Gary Da Costa\altaffilmark{2}, Amanda Karakas\altaffilmark{2}, David Yong\altaffilmark{2}, Kevin Schlaufman\altaffilmark{3}, Heather R. Jacobson\altaffilmark{3}, Qinsi Yu\altaffilmark{3}, Cherie Fishlock\altaffilmark{2}}
\altaffiltext{1}{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observatory, Chile.}
\altaffiltext{2}{Research School of Astronomy and Astrophysics, Australian National University, Canberra, ACT 2611, Australia; acasey@mso.anu.edu.au}
\altaffiltext{3}{Massachusetts Institute of Technology, Kavli Institute for Astrophysics and Space Research,
77 Massachusetts Avenue, Cambridge, MA 02139, USA}
\altaffiltext{4}{Departamento de Astronom\'ia y Astrof\'isica, Ponticia Universidad Cat\'olica de Chile, Av. Vicu\~na Mackenna 4860, Macul, 782-0436 Santiago, Chile}

\begin{abstract}
\noindent{}We present a detailed analysis of high $S/N$, high-resolution spectra for 5 Aquarius stream stars observed with the MIKE spectrograph on the Magellan Clay telescope. Our sample represents one third of the 15 members in the stream. We find the stream is not mono-metallic; the metallicity ranges from [Fe/H] = $-$0.63 to $-$1.58 dex. No anti-correlation in Na-O abundances is present, and we find a strong positive Mg-Al relationship, similar to that observed in the thick disc. We find no evidence that the stream is a result of a disrupted classical globular cluster, contrary to a previously published claim. High [(Na, Ni, $\alpha$)/Fe] and low [Ba/Y] abundance ratios in the stream suggests it is not a tidal tail from a disrupted dwarf galaxy, either. The stream is chemically indistinguishable from Milky Way field stars with the exception of one candidate, C222531-145437. From its position, velocity, and detailed chemical abundances, C222531-145437 is likely a star that was tidally disrupted from $\omega$-Centauri. We propose the Aquarius stream is galactic in origin, and could be the result from a disc-satellite perturbation in the Milky Way thick disc on the order of a few gigayear ago. Derived orbits, $UVW$ velocities, and angular momenta of the Aquarius members offer qualitative support for our hypothesis. Assuming C222531-145437 is a tidally disrupted member of $\omega$-Centauri, this system is the most likely disc perturber. In the absence of compelling chemical and/or dynamical evidence that the Aquarius stream is the tidal tail of a disrupted satellite, we advocate the ``Aquarius group'' as a more appropriate description. Like the Canis Major over-density, as well as the Hercules and Monoceros groups, the Aquarius group adds to the list of kinematically-identified substructures that are not actually accreted material; they are simply part of the rich complexity of the Milky Way structure.
\end{abstract}

@@

\section{Introduction}
Galaxies are formed hierarchically through chaotic mergers of smaller systems, and the Milky Way is no exception \citep{bullock;johnston_2005,helmi_2008}. The accumulating stellar debris in our own Galactic halo provides ongoing evidence for such merging events \citep[e.g.][]{bell;et-al_2008}. As satellites fall towards the Galaxy, tidal forces disrupt the system, hurtling stars in leading and trailing directions. The position and velocities of stars within these ``stellar streams'' are sensitive to the Galactic potential. As such, their phase-space information can collectively constrain the fraction and distribution of accreted matter in the galaxy, the sub-halo mass function, as well as the shape and extent of the Milky Way's dark matter halo. Additionally, individual chemical abundances can trace the chemical evolution of the Galaxy and its satellite systems.

Wide-field deep imaging surveys have proved excellent sources for finding stellar streams \citep[e.g.][]{belokurov;et-al_2007}. Dozens of streams have been identified through careful photometric selections and matched-filtering techniques, with some to a galactocentric distance of 100\,kpc \citep[e.g., see][]{drake;et-al_2013}. Indeed, it is clear that a large fraction of the stellar halo has been built up by accretion. However, as \citet{helmi;white_1999} point out, these detection strategies are most successful for identifying streams that are sufficiently distant from the solar neighbourhood. A nearby stream, within $\sim$10\,kpc, will not appear as a photometric over-density because the stars would be sparsely positioned across the sky. Such substructures would only be detectable by their kinematics, or perhaps with precise elemental abundances through a ``chemical tagging'' approach (e.g. see \citealt[][]{freeman;bland-hawthorn_2002}). The confirmation of such substructures would serve to substantially increase the fraction of the known accreted material in the Galaxy.

It is therefore necessary to spectroscopically survey stars in the solar neighbourhood to reveal any nearby substructures. The Radial Velocity Experiment (RAVE) team began such a survey in 2003 and has taken spectra of over 500,000 stars across 17,000\,deg$^{2}$ \citep{steinmetz;et-al_2006}. The primary goal of RAVE is to obtain radial velocities for stars in the solar neighbourhood and beyond. In an attempt to remain kinematically unbiased, RAVE candidates were selected solely by their apparent magnitude ($9 < I < 13$).  Almost all of these candidates have published radial velocities \citep{steinmetz;et-al_2006}, and for a subset of stars with a sufficient signal-to-noise ($S/N$) ratio, stellar parameters have been derived by a $\chi^2$-minimisation technique \citep{zwitter;et-al_2008, siebert;et-al_2011}.

Using these data, \citet{williams;et-al_2011} identified a co-moving group of nearby (${0.5\,\mbox{kpc} \lesssim D \lesssim 10\,\mbox{kpc}}$) stars near ${(l, b) = (60^\circ, -55^\circ)}$, in the vicinity of the Aquarius constellation. Thus, the co-moving group was named the Aquarius stream. The stream is most apparent when examining heliocentric velocities against galactic latitude for stars within $-70^\circ < b < -50^\circ$. \citet{williams;et-al_2011} employed a selection criteria of $-250\,\mbox{km s}^{-1} < V_{\rm hel} < -150\,\mbox{km s}^{-1}$, $30^\circ < l < 75^\circ$ and $J > 10.3$ to maximize the contrast between the stream and stellar background, identifying 15 stars in the process. The average heliocentric velocity of these members was found to be $V_{\rm hel} = -199\,\mbox{km s}^{-1}$, with a dispersion of 27\,km s$^{-1}$. The radial velocity uncertainties provided by the RAVE catalog are described to be $\sim$2\,km s$^{-1}$, so the stream's wide velocity distribution appears to be real.

Through a statistical comparison with predictions of stellar positions and kinematics from the Galaxia \citep{sharma;et-al_2011} and Besan\c{c}on \citep{robin;et-al_2003} models of the Milky Way, \citet{williams;et-al_2011} found the stream \ to be statistically significant ($>4\sigma$). The choice of model, cell dimension, or extinction rate made no real difference to the detection significance. The authors concluded the over-density was genuine, and inferred that the co-moving group is a stellar stream. Based on the phase space information available, \citet{williams;et-al_2011} concluded that the newly discovered stream could not be positively associated with the Sagittarius or Monoceros stream, the Hercules-Aquila cloud, or either the Canis Major or Virgo over-densities.

RAVE data suggest the Aquarius stream has a metallicity of [Fe/H] $= -1.0 \pm 0.4$\,dex\footnote{\citet{williams;et-al_2011} formally quote [M/H], but for the sake of a consistent discussion we assume [M/H] $\equiv$ [Fe/H] throughout this study.}, slightly more metal-rich than halo stars at the same distance (${\mbox{[Fe/H]} = -1.1 \pm 0.6}$\,dex) after the same selection cuts had been employed. Of the 15 Aquarius stream stars in the \citet{williams;et-al_2011} discovery sample, the metallicity range determined from medium-resolution spectroscopy is wide: from [Fe/H] = --2.02 to --0.33. High-resolution spectra with high $S/N$ are necessary to accurately characterise the stream's metallicity distribution function (MDF).

To this end, \citet{wylie-de-boer;et-al_2012} obtained high-resolution ($\mathcal{R} = 25,000$) spectra with modest $S/N$ ($\sim$30 pixel$^{-1}$) for six Aquarius stream stars using the echelle spectrograph on the Australian National University's 2.3m telescope. Their data indicate a surprisingly narrow spread in metallicity compared to previous work: ${\mbox{[Fe/H]} = -1.09 \pm 0.10}$\,dex, with a range extending only from $-1.25$ to {--0.98\,dex}. Samples with such small dispersions in metallicity are typically observed in mono-metallic environments (e.g. globular or open clusters). The largest [Fe/H] discrepancy between the \citet{williams;et-al_2011} and \citet{wylie-de-boer;et-al_2012} study was ${\Delta\mbox{[Fe/H]} = -0.66}$\,dex for the most metal-rich star in the \citet{williams;et-al_2011} sample. The most metal-poor star in the \citet{williams;et-al_2011} study was not observed by \citet{wylie-de-boer;et-al_2012}.

In addition to ascertaining stellar parameters, \citet{wylie-de-boer;et-al_2012} measured elemental abundances for the Aquarius stream stars -- the only study to date to do so. The authors primarily focussed on Na, O, Mg, Al, and Ni. These elements have been extensively studied in globular cluster stars, where unique abundance patterns are observed. Specifically, an anti-correlation between sodium and oxygen content appears ubiquitous to stars in globular clusters \citep{carretta;et-al_2009a}. \citet{wylie-de-boer;et-al_2012} identified two stream stars with slightly higher [Na/Fe] abundance ratios than halo stars of the same metallicity. No strong oxygen depletion was evident in the data, and no overall {Na-O} anti-correlation was present. \citet{wylie-de-boer;et-al_2012} also found [Ni/Fe] abundance ratios similar to thick disk/globular cluster stars, markedly higher than those reported for the Fornax dwarf spheroidal (dSph) galaxy, which has a comparable mean metallicity to the Aquarius stream.

Combined with the low level of [Fe/H] scatter present in their sample, these chemical abundances led \citet{wylie-de-boer;et-al_2012} to conclude that the Aquarius stream is the result of a tidally disrupted globular cluster. However, \citet{williams;et-al_2011} previously excluded this scenario after modelling an Aquarius-like progenitor infalling onto the Milky Way. The predicted positions and velocities from their simulations did not match any known globular cluster. If both scenarios are accurate, then the undiscovered disrupting cluster might still remain. It should also be quite close, such that its continued absence would be puzzling.

We seek to investigate the nature of the Aquarius stream, specifically the  globular cluster origin claimed by \citet{wylie-de-boer;et-al_2012}. Details of the observations and data reduction  are outlined in the following section. The bulk of our analysis is presented in Section \ref{sec:analysis} and a thorough chemical abundance analysis is chronicled separately in Section \ref{sec:chemical-abundances}. Uncertainties are outlined in Section \ref{sec:uncertainties}. A detailed discussion of our results is made in Section \ref{sec:discussion}, and we conclude in Section \ref{sec:conclusions} with a summary of our conclusions and critical interpretations.

\begin{deluxetable*}{lccccccccccc}
\tablecolumns{1}
\tabletypesize{\scriptsize}
\tablecaption{Observations\label{tab:observations}}
\tablehead{
    \colhead{Designation} &
	\colhead{$\alpha$} &
	\colhead{$\delta$} &
	\colhead{UT} &
	\colhead{UT} &
	\colhead{Airmass} &
	\colhead{Seeing} &
	\colhead{$t_{exp}$} &
	\colhead{S/N\tablenotemark{a}} &
	\colhead{$V_{\rm hel}$} \\
 & (J2000) & (J2000) & Date & Time & & (\arcsec) & (secs) & (px$^{-1}$) & (km s$^{-1}$) 
}
\startdata

\\ \multicolumn{11}{c}{Standard Stars} \\ \hline \\
HD\,41667	& 06:05:03.7 & $-$32:59:36.8	& 2011-03-13	& 23:40 & 1.01	& 1.0 & 90 	& 340 & 297.1 		\\
HD\,44007	& 06:18:48.6 & $-$14:50:44.2 	& 2011-03-13	& 23:52 & 1.03	& 1.0 & 120	& 280 & 161.8 		\\
HD\,76932	& 08:58:44.2 & $-$16:07:54.2	& 2011-03-14	& 00:16 & 1.16	& 1.0 & 25	& 330 & 117.8		\\
HD\,136316	& 15:22:17.2 & $-$53:14:13.9	& 2011-03-14	& 09:37 & 1.12	& 0.9 & 120 	& 400 & $-$38.8 	\\
HD\,141531	& 15:49:16.9 & $+$09:36:42.5	& 2011-03-14	& 09:52 & 1.31	& 0.9 & 120	& 350 & 2.8		\\
HD\,142948	& 16:00:01.6 & $-$53:51:04.1	& 2011-03-14	& 09:45 & 1.11	& 1.0 & 90 	& 320 & 29.9 		\\
\hline

\\ \multicolumn{11}{c}{Program Stars} \\ \hline \\
C222531-145437	& 22:25:31.7 & $-$14:54:39.6	& 2011-07-30	& 06:52 & 1.03	& 0.8	& 650 & 135	& $-$156.4 \\
C230626-085103	& 23:06:26.6 & $-$08:51:04.8	& 2011-07-30	& 08:15 & 1.10	& 1.0	& 650 & 100	& $-$221.1 \\
J221821-183424	& 22:18:21.2 & $-$18:34:28.3	& 2011-07-30	& 05:58 & 1.03	& 0.9 	& 650 & 115	& $-$159.5 \\
J223504-152834	& 22:35:04.5 & $-$15:28:34.9	& 2011-07-30 & 07:34 & 1.05	& 1.0 	& 650 & 130	& $-$169.7 \\
J223811-104126	& 22:38:11.6 & $-$10:41:29.4	& 2011-07-30	& 08:57 & 1.22	& 1.2 	& 650 & 115	& $-$235.7

@@

% V-band magnitudes from APASS
%C222531-145437 
%RA	RAerr*	Dec.	Dec. err*	# of Obs.	Johnson V	Verr	Johnson B	Berr	Sloan g'	g'err	Sloan r'	r'err	Sloan i'	i'err
%336.381962	0.726	-14.910536	0.191	11	12.51	0.076	13.709	0.046	13.066	0.031	12.154	0.159	11.718	0.054

%C230626-085103
%346.610635	0.593	-8.851072	0.195	11	12.601	0.037	13.885	0.046	13.208	0.027	12.189	0.055	11.762	0.037

%22:18:21-183424
%334.588459	0.442	-18.573525	0.14	18	12.116	0.035	13.072	0.031	12.569	0.018	11.822	0.037	11.508	0.031

%22:35:04 -15:28:34.9
%338.76827	0.597	-15.476482	0.152	8	12.26	0.027	13.281	0.022	12.731	0.021	11.935	0.054	11.608	0.044

% 223811-104126
%339.547668	0.583	-10.691316	0.096	9	11.933	0.024	12.718	0.096	12.309	0.025	11.709	0.036	11.461	0.044

\section{Observations \& Data Analysis}
